---
title: "Visualization and Analysis of Personal Medical Cost Dataset"
author: "Koki Ando"
date: "3/15/2018"
output:
  html_document:
    code_folding: show
    highlight: tango
    theme: cosmo
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preparation
I found a interesting datase on kaggle [Medical Cost Personal Datasets
](https://www.kaggle.com/mirichoi0218/insurance)
```{r}
library(tidyverse)
library(gganimate)
library(data.table)
library(plotly)

insurance <- fread("https://s3-ap-southeast-2.amazonaws.com/koki25ando/insurance.csv", data.table = FALSE)
insurance$smoker <- as.factor(insurance$smoker)
```

## Visualization

### Violin plot
```{r}
insurance %>% 
  ggplot(aes(x=smoker, y = charges, fill = smoker, colour = smoker)) + 
  geom_violin()
```

### Scatter plot

```{r}
insurance %>% 
  ggplot(aes(x= bmi, y= charges, colour = smoker)) + geom_point() + 
  geom_smooth(method="lm")
```

These two visualizations show us there are huge differnces between smokers and non-smokers.
So after next animation plot, im gonna focus on bmi variables of smokers. 


### Animation Scatter plot


```{r}
insurance %>%
  plot_ly(x = ~bmi, y = ~charges, color = ~smoker, size = ~children, frame = ~age,
          type = 'scatter', mode = 'markers', showlegend = T)
```

## Analysis

### Prediction of smokers' health care cost


```{r}
insurance.smoker <- insurance %>% filter(smoker == "yes")
fit <- lm(charges ~ bmi, data = insurance.smoker)

fit
```

example 1) bmi:30
```{r}
x = 30
charge.amount <- 1473*x + -13187
charge.amount
```